\startcomponent sketch_of_the_six_languages

\chapter{Dogma Regarding the Interpretation of Language}

The existence of a language is proven by the medium.

All machines are constructed from language.

Languages without interpretation are called \emph{alien languages}.

Languages without a unique interpretation are called \emph{contingent
	languages}.

There are three kinds of contingent languages: secret languages, natural
languages, and strategic languages.

Languages with a unique interpretation are called \emph{formal languages}.

There are three kinds of formal languages: noncomputable languages, computable
languages, and unsafe languages.

\rule

Secret languages are the languages spoken by the mind to itself.

All decisions are made by applying the mechanism of universal translation to
secret languages.

All translations of secret languages that are complete are also \emph{alien}.

\rule

Natural languages are formed using the mechanism of universal translation to
construct a sequence of at least three decisions.

Natural language that can be interpreted as an indivisible decision is called
strategic language.

All contingent languages composed of discrete symbols are strategic.

The decisions that are represented by strategic language are called
\emph{strategic decisions}.

All strategic languages are formed from natural languages using the principle
of universal empathy.

When an interpretation of natural language is contingent on strategic language,
the interpretation is referred to as \emph{dogma}.

\rule

All formal languages can be built from secret languages using the calculus of
constructions.

Noncomputable language is a formal language that can be interpreted as
strategic language.

Computable language is a formal language that can be translated into the
transformations of a medium.

All computable languages can be interpreted as noncomputable language.

Computable language that can be translated into a decision is called unsafe
language.

When all translations of an unsafe language are alien, an arbitrary translation
may be referred to as an \emph{executable}.

When the interpretation of an unsafe language is assumed to be independent of
contingent language, the interpretation is referred to as a \emph{program}.

When the interpretation of an unsafe language is contingent on strategic
language, the interpretation is referred to as a \emph{contract}.

The decisions that are translated from unsafe language are called \emph{unsafe
	decisions}.

All unsafe decisions are strategic decisions.

\stopcomponent
